### 2016-07-15 2016_Proceedings_ISMIR/papers.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface
fixed inconsistencies in a few authors' names

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 1: Mixed}
\includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 2: Rhythm}
\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
\includepaper{Bayesian Meter Tracking on Learned Signal Representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich, Meinard Mueller}{articles/022_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 3: Users}
\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 2}
\includepdf[pages=4,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{Known Artist Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich, Meinard Mueller}{articles/098_Paper}

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 4: Musicologies}
\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 5: Structure}
\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 3}
\includepdf[pages=8,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{An Analysis of Agreement in Classical Music Perception and its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}

>>>>

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 1: Mixed}
\includepdf[pages=4,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{T. P. Vinutha, Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 2: Rhythm}
\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
\includepaper{Bayesian Meter Tracking on Learned Signal Representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Prätzlich, Meinard Mueller}{articles/022_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 3: Users}
\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 2}
\includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{Known Artist Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Prätzlich, Meinard Mueller}{articles/098_Paper}

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 4: Musicologies}
\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 5: Structure}
\includepdf[pages=8,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 3}
\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

@@

\includepaper{An Analysis of Agreement in Classical Music Perception and its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
